


## Specific Aims 1: To compare the demographic features of the sample from the first study to that of the second study qualitatively and quantitatively.

### 1.1. Gather descriptive statistics of all the variables in the first study

```{r}
#gender vs response
gender_table = data.frame(Yes = c(173, 39), No = c(148, 61), Total = c(321, 100))
row.names(gender_table) = c("Male", "Female")
y = as.matrix(gender_table)
x = barplot(y, main = "Population Distribution by Gender and Response", xlab = "Response", ylim = c(0, 350), col = c("blue", "yellow"), legend.text = TRUE, args.legend = list(x = ncol(gender_table) - 0.1, bty = "n"), beside = TRUE)
text(x, y+15, labels = as.character(y))
```


```{r}
y <- c(173,148,39,61)
Response <- gl(2,1,4,labels=c("Yes","No"))
Gender <- gl(2,2,labels=c("Male","Female"))
gender_t2 <- data.frame(y,Response,Gender)
ov = xtabs(y ~ Gender + Response)
prop.test(ov) #Pearson's X2 test: p < 0.05, reject the H0 of independence, so response is significantly associated with gender
mod1 = glm(y ~ Gender + Response, poisson)
library(faraway)
sumary(mod1)
pchisq(deviance(mod1), df = 1, lower.tail = FALSE) #deviance based test generate similar results
```




```{r}
race_table = data.frame(Yes = c(189, 23), No = c(172, 37), Total = c(361, 60))
row.names(race_table) = c("White", "Not white")
y = as.matrix(race_table)
x = barplot(y, main = "Population Distribution by Race and Response", xlab = "Response", ylim = c(0, 400), col = c("blue", "yellow"), legend.text = TRUE, args.legend = list(x = ncol(race_table) + 0.2, bty = "n"), beside = TRUE)
text(x, y+15, labels = as.character(y))
```


```{r}
y <- c(189, 172, 23, 37)
Response <- gl(2,1,4,labels=c("Yes","No"))
Race <- gl(2,2,labels=c("White","Not white"))
race_t2 <- data.frame(y,Response,Race)
ov = xtabs(y ~ Race + Response)
prop.test(ov) #Pearson's X2 test: marginally significant
mod2 = glm(y ~ Race + Response, poisson)
sumary(mod2)
pchisq(deviance(mod2), df = 1, lower.tail = FALSE) #deviance based test is preferred, p<0.05, so response is significantly associated with race
```




```{r}
marital_table = data.frame(Yes = c(2, 210), No = c(56, 153), Total = c(58, 363))
row.names(marital_table) = c("Married", "Other")
y = as.matrix(marital_table)
x = barplot(y, main = "Population Distribution by Marital Status and Response", xlab = "Response", ylim = c(0, 420), col = c("blue", "yellow"), legend.text = TRUE, args.legend = list(x = ncol(marital_table), bty = "n"), beside = TRUE)
text(x, y+15, labels = as.character(y))
```


```{r}
y <- c(2, 56, 210, 153)
Response <- gl(2,1,4,labels=c("Yes","No"))
Marital <- gl(2,2,labels=c("Married","Other"))
marital_t2 <- data.frame(y,Response,Marital)
ov = xtabs(y ~ Marital + Response)
prop.test(ov) #Pearson's X2 test: significant
mod3 = glm(y ~ Marital + Response, poisson)
sumary(mod3)
pchisq(deviance(mod3), df = 1, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with marital status

#We found that marital status, gender, and race are significant predictors.
```



```{r}
job_table = data.frame(Yes = c(43, 6, 141, 2, 20), No = c(12, 2, 134, 61, 0), Total = c(55, 8, 275, 63, 20))
row.names(job_table) = c("White collar", "Blue Collar", "Student", "House", "Unemployed/Unknown")
y = as.matrix(job_table)
x = barplot(y, main = "Population Distribution by Job and Response", xlab = "Response", ylim = c(0, 420), col = c("white", "blue", "yellow", "green", "red"), legend.text = TRUE, args.legend = list(x = ncol(job_table) + 7, y = 420, bty = "n"), beside = TRUE)
text(x, y+15, labels = as.character(y))
```


```{r}
y <- c(43, 12, 6, 2, 141, 134, 2, 61, 20, 0)
Response <- gl(2,1,10,labels=c("Yes","No"))
Job <- gl(5,2,labels=c("White","Blue", "Student", "House", "Unemployed/Unknown"))
job_t2 <- data.frame(y,Response,Job)
ct= xtabs(y ~ Job + Response, job_t2)
prop.test(ct)
mod4 = glm(y ~ Job + Response, poisson, ct)
sumary(mod4)
pchisq(deviance(mod4), df = 4, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with job status
mosaicplot(ct, color=TRUE, main=NULL, las=1) #mosaic plot
```






```{r}
education_table = data.frame(Yes = c(197, 15), No = c(152, 57), Total = c(349, 72))
row.names(education_table) = c("College and more", "Lower than college")
y = as.matrix(education_table)
x = barplot(y, main = "Population Distribution by Education and Response", xlab = "Response", ylim = c(0, 380), col = c("blue", "yellow"), legend.text = TRUE, args.legend = list(x = ncol(education_table) + 1.6, bty = "n"), beside = TRUE)
text(x, y+15, labels = as.character(y))
```


```{r}
y <- c(197, 152, 15, 57)
Response <- gl(2,1,4,labels=c("Yes","No"))
Education <- gl(2,2,labels=c("College and more","Lower than college"))
edu_t2 <- data.frame(y,Response,Education)
ov = xtabs(y ~ Education + Response)
prop.test(ov) #Pearson's X2 test: significant
mod5 = glm(y ~ Education + Response, poisson)
sumary(mod5)
pchisq(deviance(mod5), df = 1, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with education status
```



```{r}
mortgage_table = data.frame(Yes = c(2, 210), No = c(21, 188), Total = c(23, 398))
row.names(mortgage_table) = c("Mortgage", "No mortgage")
y = as.matrix(mortgage_table)
x = barplot(y, main = "Population Distribution by Mortgage Status and Response", xlab = "Response", ylim = c(0, 450), col = c("blue", "yellow"), legend.text = TRUE, args.legend = list(x = ncol(mortgage_table) + 0.8, bty = "n"), beside = TRUE)
text(x, y+15, labels = as.character(y))
```

```{r}
y <- c(2, 21, 210, 188)
Response <- gl(2,1,4,labels=c("Yes","No"))
Mortgage <- gl(2,2,labels=c("Mortgage","No mortgage"))
mortgage_t2 <- data.frame(y,Response,Mortgage)
ov = xtabs(y ~ Mortgage + Response)
prop.test(ov) #Pearson's X2 test: significant
mod6 = glm(y ~ Mortgage + Response, poisson)
sumary(mod6)
pchisq(deviance(mod6), df = 1, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with mortgage status
```


```{r}
delinquency_table = data.frame(Yes = c(146, 66), No = c(39, 170), Total = c(185, 236))
row.names(delinquency_table) = c("more than 60 days", "60 or less days")
y = as.matrix(delinquency_table)
x = barplot(y, main = "Population Distribution by Delinquency and Response", xlab = "Response", ylim = c(0, 450), col = c("blue", "yellow"), legend.text = TRUE, args.legend = list(x = ncol(delinquency_table) + 1.7, bty = "n"), beside = TRUE)
text(x, y+15, labels = as.character(y))
```


```{r}
y <- c(146, 39, 66, 170)
Response <- gl(2,1,4,labels=c("Yes","No"))
Delinquency <- gl(2,2,labels=c("more than 60 days","60 or less days"))
delinquency_t2 <- data.frame(y,Response,Delinquency)
ov = xtabs(y ~ Delinquency + Response)
prop.test(ov) #Pearson's X2 test: significant
mod7 = glm(y ~ Delinquency + Response, poisson)
sumary(mod7)
pchisq(deviance(mod7), df = 1, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with delinquency status
```



```{r}
phone_table = data.frame(Yes = c(116, 96), No = c(35, 174), Total = c(151, 270))
row.names(phone_table) = c("Cell phone", "Other")
y = as.matrix(phone_table)
x = barplot(y, main = "Population Distribution by Primary Phone and Response", xlab = "Response", ylim = c(0, 450), col = c("blue", "yellow"), legend.text = TRUE, args.legend = list(x = ncol(phone_table) - 0.4, bty = "n"), beside = TRUE)
text(x, y+15, labels = as.character(y))
```


```{r}
y <- c(116,35,96,174)
Response <- gl(2,1,4,labels=c("Yes","No"))
Phone <- gl(2,2,labels=c("Cell phone","Other"))
phone_t2 <- data.frame(y,Response,Phone)
ov = xtabs(y ~ Phone + Response)
prop.test(ov) #Pearson's X2 test: significant
mod8 = glm(y ~ Phone + Response, poisson)
sumary(mod8)
pchisq(deviance(mod8), df = 1, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with primary phone
```


### 1.2 Descriptive statistics of the nine variables representing demographic features in the second study

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(data.table)
library(tibble)
library(GGally)
#library(kableExtra) #can't load the package on my computer
library(ggpubr)

#Read in Data
raw_data = read_csv("prac_data.csv") %>%
  mutate(
    price = unlist(read_csv("price.csv")),
    job = replace(job, which(job == "unknown"),"Unknown"),
    job = as.factor(replace_na(job,"Unknown")),
    education = replace_na(education,"Unknown"),
    education = replace(education,which(education == "unknown"),"Unknown"),
    contact = replace_na(contact,"Unknown"),
    contact = replace(contact,which(contact == "unknown"),"Unknown"),
    pdays = replace_na(pdays,-1),
    default = replace_na(default,"Unknown"),
    marital = replace_na(marital,"Unknown"),
    housing = replace_na(housing,"Unknown"),
    loan = replace_na(loan,"Unknown"),
    previous = replace_na(previous,0),
    poutcome = replace_na(poutcome,"Unknown"),
    inPrevious = if_else(previous > 0,TRUE,FALSE),
    numMissing = rowSums(across(everything(), ~is.na(.)))
  )
numericColumns = c(1,6,10,12,13,14,15,18)
categoricalColumns = c(2,3,4,5,7,8,9)
df_colnames = colnames(raw_data)
```

```{r}
raw_data$marital = as.factor(raw_data$marital)
raw_data$education = as.factor(raw_data$education)
raw_data$default = as.factor(raw_data$default)
raw_data$housing = as.factor(raw_data$housing)
raw_data$loan = as.factor(raw_data$loan)
raw_data$contact = as.factor(raw_data$contact)
raw_data$poutcome = as.factor(raw_data$poutcome)
raw_data$y = as.factor(raw_data$y)
summary(raw_data)
```


```{r}
levels(raw_data$y) = c("no", "yes")
counts_job = table(raw_data$job, raw_data$y)
x = barplot(counts_job, ylim = c(0, 22000), main = "Population distribution by Job status and Response", xlab = "Response", col = rainbow(12), legend.text = TRUE, args.legend = list(x = "top", ncol = 3, bty = "n"), beside = TRUE)
text(x, y = c(counts_job[,1]+500, counts_job[,2]+500), labels = c(counts_job[,1], counts_job[,2]), cex = 0.6)
```


```{r}
prop.test(counts_job)
counts_job = as.data.frame(counts_job)
mod9 = glm(Freq ~ Var1 + Var2, poisson, counts_job)
sumary(mod9)
pchisq(deviance(mod9), df = 11, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with job status
```



```{r}
counts_marital = table(raw_data$marital, raw_data$y)
x = barplot(counts_marital, ylim = c(0, 35000), main = "Population distribution by Marital status and Response", xlab = "Response", col = rainbow(4), legend.text = TRUE, args.legend = list(x = "topright", bty = "n"), beside = TRUE)
text(x, y = c(counts_marital[,1] + 800, counts_marital[,2] + 800), labels = c(counts_marital[,1], counts_marital[,2]), cex = 0.8)
```


```{r}
prop.test(counts_marital)
counts_marital = as.data.frame(counts_marital)
counts_marital2 = counts_marital[!(counts_marital$Var1 == "Unknown"),] 
mod10 = glm(Freq ~ Var1 + Var2, poisson, counts_marital2)
sumary(mod10)
pchisq(deviance(mod10), df = 2, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with marital status
```


```{r}
counts_education = table(raw_data$education, raw_data$y)
x = barplot(counts_education, ylim = c(0, 35000), main = "Population distribution by Education and Response", xlab = "Response", col = rainbow(4), legend.text = TRUE, args.legend = list(x = "topright", bty = "n"), beside = TRUE)
text(x, y = c(counts_education[,1] + 800, counts_education[,2] + 800), labels = c(counts_education[,1], counts_education[,2]), cex = 0.8)
```


```{r}
prop.test(counts_education)
counts_education = as.data.frame(counts_education)
mod11 = glm(Freq ~ Var1 + Var2, poisson, counts_education)
sumary(mod11)
pchisq(deviance(mod11), df = 3, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with education
```



```{r}
counts_default = table(raw_data$default, raw_data$y)
x = barplot(counts_default, ylim = c(0, 40000), main = "Population distribution by Status of Credit in Default and Response", xlab = "Response", col = rainbow(3), legend.text = TRUE, args.legend = list(x = "topright", bty = "n"), beside = TRUE)
text(x, y = c(counts_default[,1] + 900, counts_default[,2] + 900), labels = c(counts_default[,1], counts_default[,2]), cex = 0.8)
```


```{r}
prop.test(counts_default)
counts_default = as.data.frame(counts_default)
counts_default2 = counts_default[!(counts_default$Var1 == "Unknown"),] 
mod12 = glm(Freq ~ Var1 + Var2, poisson, counts_default2)
sumary(mod12)
pchisq(deviance(mod12), df = 1, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with status of credit in default
```


```{r}
counts_housing = table(raw_data$housing, raw_data$y)
x = barplot(counts_housing, ylim = c(0, 25000), main = "Population distribution by Mortgage status and Response", xlab = "Response", col = rainbow(3), legend.text = TRUE, args.legend = list(x = "topright", bty = "n"), beside = TRUE)
text(x, y = c(counts_housing[,1] + 800, counts_housing[,2] + 800), labels = c(counts_housing[,1], counts_housing[,2]), cex = 0.8)
```



```{r}
prop.test(counts_housing)
counts_housing = as.data.frame(counts_housing)
counts_housing2 = counts_housing[!(counts_housing$Var1 == "Unknown"),] 
mod13 = glm(Freq ~ Var1 + Var2, poisson, counts_housing2)
sumary(mod13)
pchisq(deviance(mod13), df = 1, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with status of mortgage
```



```{r}
counts_loan = table(raw_data$loan, raw_data$y)
x = barplot(counts_loan, ylim = c(0, 35000), main = "Population distribution by Status of Personal Loan and Response", xlab = "Response", col = rainbow(3), legend.text = TRUE, args.legend = list(x = "topright", bty = "n"), beside = TRUE)
text(x, y = c(counts_loan[,1] + 800, counts_loan[,2] + 800), labels = c(counts_loan[,1], counts_loan[,2]), cex = 0.8)
```



```{r}
prop.test(counts_loan)
counts_loan = as.data.frame(counts_loan)
counts_loan2 = counts_loan[!(counts_loan$Var1 == "Unknown"),]
mod14 = glm(Freq ~ Var1 + Var2, poisson, counts_loan2)
sumary(mod14)
pchisq(deviance(mod14), df = 1, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with status of personal loan
```


```{r}
levels(raw_data$contact) = c("cellular", "telephone", "Unknown")
counts_contact = table(raw_data$contact, raw_data$y)
x = barplot(counts_contact, ylim = c(0, 35000), main = "Population distribution by Primary Phone and Response", xlab = "Response", col = rainbow(3), legend.text = TRUE, args.legend = list(x = "topright", bty = "n"), beside = TRUE)
text(x, y = c(counts_contact[,1] + 800, counts_contact[,2] + 800), labels = c(counts_contact[,1], counts_contact[,2]), cex = 0.8)
```


```{r}
prop.test(counts_contact)
counts_contact = as.data.frame(counts_contact)
mod15 = glm(Freq ~ Var1 + Var2, poisson, counts_contact)
sumary(mod15)
pchisq(deviance(mod15), df = 2, lower.tail = FALSE) #deviance based test, p<0.05, so response is significantly associated with primary phone
```

### 1.3. Compare the demographic features common in both studies, including age, job, marital status, education, non-mortgage loan balance, housing mortgage and primary phone.

```{r}
data1 = drop_na(raw_data, age) #create a dataset with the rows of missing value for age removed

#boxplot
library(ggplot2)
ggplot(data1, aes(x = y, y = age, fill = y)) + xlab("Response") + ylab("Age") + geom_boxplot()

bartlett.test(age ~ y, data1) #variances are not equal for groups of different responses
#Welch two sample t-test
t.test(age ~ y, data1, var.equal=FALSE, conf.level = 0.95) #means are significantly different

quantile(data1$age[data1$y == "yes"], c(0.025, 0.5, 0.975)) #compare to 25.5, close to the lower limit
quantile(data1$age[data1$y == "no"], c(0.025, 0.5, 0.975)) #compare to 37.5, close to the median
#raw_data$age[is.na(raw_data$age)] = median(raw_data$age, na.rm = TRUE)
#plot(density(raw_data$age), main = "density plot of age after imputation", xlab = "age")
```


```{r}
data2 = drop_na(raw_data, balance) #create a dataset with the rows of missing value for age removed

#boxplot
ggplot(data2, aes(x = y, y = balance, fill = y)) + xlab("Response") + ylab("Non-mortgage loan balance") + geom_boxplot()

bartlett.test(balance ~ y, data2) #variances are not equal for groups of different responses
#Welch two sample t-test
t.test(balance ~ y, data2, var.equal=FALSE, conf.level = 0.95) #means are significantly different

quantile(data2$balance[data2$y == "yes"], c(0.025, 0.5, 0.975)) #compare to 23,879, which is larger than the upper limit
quantile(data2$balance[data2$y == "no"], c(0.025, 0.5, 0.975)) #compare to 1,250, within the range
```


```{r}
#mortgage
counts_housing2 = counts_housing[!(counts_housing$Var1 == "Unknown"),] 
colnames(counts_housing2) = c("mortgage", "response", "Freq")
counts_housing2 = arrange(counts_housing2, -order(mortgage))
observed = mortgage_t2$y/421*sum(counts_housing2$Freq)
observed
G2 = 2*sum(observed*log(observed/counts_housing2$Freq)) #LRT
G2
1-pchisq(G2, df = 4-1) #proportion of people with mortgage in the 1st study is significantly different from that in the 2nd study
```


```{r}
#marital
colnames(counts_marital) = c("marital", "response", "Freq")
other_no = sum(counts_marital$Freq[which(counts_marital$response=="no" & (counts_marital$marital=="divorced"|counts_marital$marital=="single"|counts_marital$marital=="Unknown"))])
other_yes = sum(counts_marital$Freq[which(counts_marital$response=="yes" & (counts_marital$marital=="divorced"|counts_marital$marital=="single"|counts_marital$marital=="Unknown"))])
exp = c(counts_marital$Freq[6], counts_marital$Freq[2], other_yes, other_no)
exp
observed = marital_t2$y/421*sum(exp)
observed
G2 = 2*sum(observed*log(observed/exp)) #LRT
G2
1-pchisq(G2, df = 4-1)

#without Unknown
other_no2 = sum(counts_marital$Freq[which(counts_marital$response=="no" & (counts_marital$marital=="divorced"|counts_marital$marital=="single"))])
other_yes2 = sum(counts_marital$Freq[which(counts_marital$response=="yes" & (counts_marital$marital=="divorced"|counts_marital$marital=="single"))])
exp2 = c(counts_marital$Freq[6], counts_marital$Freq[2], other_yes2, other_no2)
exp2
observed2 = marital_t2$y/421*sum(exp2)
observed2
G2 = 2*sum(observed2*log(observed/exp2)) #LRT
G2
1-pchisq(G2, df = 4-1) #the proportion of people with different marital status in the 1st study is significantly different from that in the 2nd study
```


```{r}
#primary phone or contact
colnames(counts_contact) = c("contact", "response", "Freq")
other_no = sum(counts_contact$Freq[which(counts_contact$response=="no" & (counts_contact$contact=="telephone"|counts_contact$contact=="Unknown"))])
other_yes = sum(counts_contact$Freq[which(counts_contact$response=="yes" & (counts_contact$contact=="telephone"|counts_contact$contact=="Unknown"))])
exp = c(counts_contact$Freq[4], counts_contact$Freq[1], other_yes, other_no)
exp
observed = phone_t2$y/421*sum(exp)
observed
G2 = 2*sum(observed*log(observed/exp)) #LRT
G2
1-pchisq(G2, df = 4-1)
#the proportion of people with cell phone as primary phone in the 1st study is significantly different from that in the 2nd study
```



```{r}
#education
colnames(counts_education) = c("education", "response", "Freq")
#Unknown is not included for the 2nd study
other_no = sum(counts_education$Freq[which(counts_education$response=="no" & (counts_education$education=="primary"|counts_education$education=="secondary"))])
other_yes = sum(counts_education$Freq[which(counts_education$response=="yes" & (counts_education$education=="primary"|counts_education$education=="secondary"))])
exp = c(counts_education$Freq[7], counts_education$Freq[3], other_yes, other_no)
exp
observed = edu_t2$y/421*sum(exp)
observed
G2 = 2*sum(observed*log(observed/exp)) #LRT
G2
1-pchisq(G2, df = 4-1) #the proportion of people with education level college or higher in the 1st study is significantly different from that in the 2nd study
```



```{r}
#job
colnames(counts_job) = c("job", "response", "Freq")
white_no = sum(counts_job$Freq[which(counts_job$response=="no" & (counts_job$job=="admin."|counts_job$job=="management"|counts_job$job=="entrepreneur"))])
white_yes = sum(counts_job$Freq[which(counts_job$response=="yes" & (counts_job$job=="admin."|counts_job$job=="management"|counts_job$job=="entrepreneur"))])
blue_no = sum(counts_job$Freq[which(counts_job$response=="no" & (counts_job$job=="blue-collar"|counts_job$job=="technician"))])
blue_yes = sum(counts_job$Freq[which(counts_job$response=="yes" & (counts_job$job=="blue-collar"|counts_job$job=="technician"))])
un_no = sum(counts_job$Freq[which(counts_job$response=="no" & (counts_job$job=="unemployed"|counts_job$job=="Unknown"))])
un_yes = sum(counts_job$Freq[which(counts_job$response=="yes" & (counts_job$job=="unemployed"|counts_job$job=="Unknown"))])
exp = c(white_yes, white_no, blue_yes, blue_no, counts_job$Freq[21], counts_job$Freq[9], counts_job$Freq[16], counts_job$Freq[4], un_yes, un_no)
exp
observed = job_t2$y/421*sum(exp)
observed
X2 = sum((observed - exp)^2/exp)
X2
1-pchisq(X2, df = 10-1)
#significantly different
```


