## Introduction

Toast has been a staple in the American breakfast for many decades.  The Millennial and Gen-Z avocado toast craze has also caused a surge in the popularity of gourmet toast.  The sustained popularity of toast as a breakfast food coupled with recent trends putting toast at the center of a health-craze created a potentially high-potential market space to combine toast with technology.  Toast Co. is aiming to capitalize on a first-mover advantage and explore this new potential market space at the intersection of toast and technology. Thus,  our  client,  Toast  Co.,  has  created  the Toast-USB which enables individuals to curate gourmet, artisanal toast right from their computer.  


Our  aim  is  to  assist  Toast  Co. to  make  informed,  data-driven  decisions  re-garding the launch of Toast-USB.  The Design of Experiments Team (DOE) conducted a first round market analysis from five metropolitan areas. Preliminary results were so promising that the DOE has conducted another larger-scale study to determine the likelihood of success of Toast-USB.  During the course ofthis investigation, we will synthesize the key findings from the first and secondstudy, perform a risk-benefit analysis on continuation of the campaign, providea binary recommendation for launch of the product,  and outline top grossingmarket demographics, and determine an optimal Manufacture Suggested Retail Price.  To accomplish this, we performed preliminary data processing and exploratory analysis to select demographic variables that have a significant impact on a person's likelihood of having a favorable response to the Toast-USB.  Then, we built a logistic model which assigned a binary (Y/N) response prediction representing if a person had a favorable response to the toaster.  Next, we used the model to determine the MSRP.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(data.table)
library(tibble)
library(GGally)
library(kableExtra)
library(ggpubr)
library(reshape2)

# <Library imported prior to call
# inserts two dataframe objects into enviroments
# imputedData which is data set with an imputed median for continous variables
# raw_data which is the data frame gained from imported the practicum 2 materials

source("data_cleaning.R")

```

## Specific Aims 2:To recommend on whether the client should move forward with the campaign and provide suggestions on campaign strategies.



```{r}
logisticRegressionModel = 

```










## 2.3  Build a logistic regression model with the binary response variable ifrespondents is willing to purchase the product, and include all of theother variables as explanatory variables.  Perform model selection to choose the optimal model.
```{r logisticregressionmodels}
# Divide the data in two, by random sampling of rows (without bootstrapping)
set.seed(333)
select.rows <- sample(1:nrow(imputedData), replace=FALSE,
                      size=floor(nrow(imputedData)/2))
# That half of the data set will now be used for selection
train.set <- imputedData[select.rows,]
# The other half will be used for inference later
test.set <- imputedData[-select.rows,]

# Fit Multiple Regression Models:
# Do not use campaign, build a test and train set


glm.prob1 = predict(glm1, newdata = test.set, type = "response")
glm.pred = ifelse(glm.prob1 > 0.5, "Yes", "No")


summary(glm1)

```

## 2.4.  In order to determine whether the campaign should move forward,estimate  the  overall  positive  response  rate  and  compare  it  to  the break-even response rate of 24.13%.

## 2.5 Identify potential high-revenue demographic groups that the client should focus the campaign on as well as providing suggestionson targeted marketing strategies.